Estimating Output Loss due to being Unrecognized as States

### 2018-12-25 paper/paper.tex
Describe the model and the equation for prediction #1

\section{Introduction}
\section{Methodology}
\section{Results}
\section{Conclusions}

\begin{thebibliography}{99}                                                                                                %
\bibitem{} 
\end{thebibliography}

>>>>

\section{Introduction}
\section{Methodology}
We model GDP per capita in territory $i$ in year $t$, denoted by $y_{it}$, as follows:
\begin{equation}\label{gdppc}
y_{it} = \beta L_{it} + \mu_i + \eta_t + \varepsilon_{it},
\end{equation}
where $L_{it}$ is the average nighttime light intensity in territory $i$ in year $t$, $\mu_i$ the territory fixed effect, $\eta_t$ the year fixed effect, and $\varepsilon_{it}$ the error term.
We also model the average GDP per capita over the sample period in territory $i$, denoted by $\bar{y}_i$ as:
\begin{equation}\label{meangdp}
\bar{y}_i = \alpha + \gamma \bar{L}_{i} + \xi_{i},
\end{equation}
where $\bar{L}_{i}$ is the nighttime light intensity in territory $i$ averaged over the sample period and $\xi_i$ the error term.

GDP per capita in unrecognized state $k$ in year $t$, denoted by $\hat{y}_{kt}$, will then be predicted as follows:
\begin{equation}
\hat{y}_{kt} = \hat{\beta} L_{kt} + \hat{\mu}_k + \hat{\eta_t},
\end{equation}
where $\hat{\beta}$ and $\hat{\eta_t}$ are the estimated $\beta$ and $\eta_t$ in equation (\ref{gdppc}). The term $\hat{\mu}_k$ is given by
\begin{equation}
\hat{\mu}_k = \hat{\alpha} + \hat{\gamma} \bar{L}_{k},
\end{equation}
where $\hat{\alpha}$ and $\hat{\gamma}$ are the estimated $\alpha$ and $\gamma$ in equation (\ref{meangdp}).

To estimate equations (\ref{gdppc}) and (\ref{meangdp}), we use the balanced panel of countries from 1992 to 2013, to avoid compositional bias in the estimation of territory and year fixed effects, $\mu_i$ and $\eta_t$. 
Standard errors are clustered both at the territory level and at the year level by using Cameron et al.\ (2011).
\section{Results}
\section{Conclusions}

\begin{thebibliography}{99}                                                                                                %
\bibitem{} Cameron, A. Colin, Jonah B. Gelbach, and Douglas L. Miller. 2011. ``Robust Inference With Multiway Clustering.'' \textit{Journal of Business \& Economic Statistics}, 29(2): 238-249.	
\end{thebibliography}
